A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
fixing tilde character.

\begin{table}[ht]
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 18.49 \\ \hline
    C4.5 & 18.84 \\ \hline
    Bayesian Networks (Simulated Annealing) & 19.15 \\ \hline
    Bayesian Networks (Hill Climbing) & 20.03 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Random Forest & 21.01 \\ \hline
    Bayesian Networks (Genetic Search) & 21.26 \\ \hline
    CART & 21.34 \\ \hline
    \end{tabular}
    \label{tbl:overall_results}
    \end{center}
\end{table}
}

>>>>

\begin{table}[ht]
    \begin{center}
    \begin{tabular}{ | l | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} & \textbf{Time} \\ \hline
    CN2 & 15.20 & 03m29s \\ \hline
    ID3 & 15.68 & 00m14s \\ \hline
    ADTree & 18.49 & 01m12s \\ \hline
    C4.5 & 18.84 & 00m08s \\ \hline
    Bayesian Networks (Simulated Annealing) & 19.15 & 00m07s \\ \hline
    Bayesian Networks (Hill Climbing) & 20.03 & 00m07s \\ \hline
    ILP (Aleph) & 20.45 & $\sim$6hours \\ \hline
    Random Forest & 21.01 & 00m08s \\ \hline
    Bayesian Networks (Genetic Search) & 21.26 & 00m04s \\ \hline
    CART & 21.34 & 07m05s \\ \hline
    \end{tabular}
    \label{tbl:overall_results}
    \end{center}
\end{table}
}
